---
title: "Levy Replication"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LoMo)
library(ws.data)
library(lubridate)
library(dplyr)
library(ggplot2)
```


```{r, echo=FALSE}
x <- gather_data()
```

##Introduction
Welcome to Liam and David's replication paper. In this segment we will be attempting, and failing badly, at replicating the results of Levy's "Relative Strength as a Criterion for Investment Selection". Thus far, we have attempted to replicate two of the three variables used for the analysis in the paper. In addition, there will be a literature review section where we engage in a lively conversation about similar pieces of work. 


##4/C Ratio
The 4/C Ratio is a performance ratio and is calculated by taking a stocks current weekly price average and dividing it into the stocks price four weeks into the future. 

##4/C Graph
```{r}
weekly <- x %>% mutate(C4 = avg.price[week+4]/avg.price) 
weekly %>% arrange(week) %>% summarise(avg.week = mean(C4)) %>% 
    ggplot(aes(week, avg.week)) + geom_line()
```



##26/C Ratio
The 26/C Ratio is another performance ratio and is calculated by taking a stocks current weekly price average and dividing it into the stock price 26 weeks into the future. 

##26/C graph
```{r}
weekly2 <- x %>% mutate(C26 = avg.price[week+26]/avg.price)
weekly2 %>% arrange(week) %>% summarise(avg.week = mean(C26)) %>% 
    ggplot(aes(week, avg.week)) + geom_line()
```

